Make any stupid plot you want

### 2020-12-07 draft/sections/math.tex
k bits of math, feel super circular

\subsubsection{Base Space $K$}
K is a triangulizable quotient topological space.
%%insert stuff about qotient spaces....

@@

where $DT$ is the set of data types (as identified by their names) and $U$ is the set of all possible objects $x$ of all types in $DT$. This means that for each type $T\in DT$, the preimage $\pi^{1}(T)\subset U $ is the domain of $T$, and a value $x \in \pi^{1}(T)\subset U$ is an object of type $T$. Spivak then defines a schema $(C, \sigma)$ of type $\pi$, where $\pi$ is the universe of all types, such that 
\begin{equation}
\sigma: C \rightarrow DT
\end{equation}
where $C$ is a finite ordered set of columns in a database. We extend C to refer to the names of all distinct

Given $F = X_{0} \times X_{1} \times \ldots \times X_{n}$, where $X_{0}, X_{1}, \ldots X_{n}$ are measurement spaces (e.g. ints, floats, colors): 
\begin{equation}
g(k) = (x_0, x_1, \ldots x_n) \text{ where } x_0 \in X_0, x_1 \in X_1, \ldots x_n \in X_n
\end{equation}

\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2f.png}
    \label{fig:}
\end{figure}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_3f.png}
\end{figure}
%%% might 
The fibers $F$ are a topological space embedded in $E$ on which lie the set of all possible values. For example, if $F$ is the interval $[0, 1]$, then $g(k)$ from equation~\ref{eq:sigma} returns a single measurement $x$ in the interval $F$:
\begin{equation}
    \label{eg:goff}
    g(k) = x, \text{ where } 0\leq x \leq 1
\end{equation}

@@

% schema is ordered list of Column, type is approx F, U cross C over sigma, 
% space of rows/records f:k -> r, sigma:k -> r, is the table function (dataframe as instance)

@@

\subsubsection{Visual Encodings}
Tau can preserves the measurement type properties (group scales)

>>>>

\subsubsection{Base Space $K$}

\begin{figure}
    \includegraphics{figures/sections/math/k_qspace.png}
    \label{fig:kquotient}
\end{figure}

$K$ is the quotient space of $E$, meaning it is the set of equivalence classes of elements $p$ in of $E$ defined via the map $\pi: E \rightarrow K$ that sends each point $p \in E$ to its equivalence class in $[p] \in K$ \cite{QuotientSpaceTopology2020,QuotientSpaceTopology2020}. As shown in figure~\ref{fig:kquotient}, the fibers $F$ divide $E$ into smaller spaces consisisting of $F$ and an open set neighborhood around $F$. This subdivision is projected down to the toplology $\Tau_k$

\begin{equation}
\tau_K = {U\subseteqq K: {p \in E: [p] \in U}\in \Tau_E}
\end{equation}

where $[p] \in U$ is the point $k \in K$ with an open set around it that has an open  preimage in $E$ under the surjective map $\pi: p \rightarrow [p]$.

@@

where $DT$ is the set of data types (as identified by their names) and $U$ is the set of all possible objects $x$ of all types in $DT$. This means that for each type $T\in DT$, the preimage $\pi^{1}(T)\subset U $ is the domain of $T$, and a value $x \in \pi^{1}(T)\subset U$ is an object of type $T$. Spivak then defines a schema $(C, \sigma)$ of type $\pi$, where $\pi$ is the universe of all types, such that 
\begin{equation}
\sigma: C \rightarrow DT
\end{equation}
where $C$ is a finite set of names of columns in a database or a list of attributes.

In the fiber bundle, $F$ is the cartesian product of all sets in the disjoint union $U_{\sigma}$

\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2f.png}
    \label{fig:}
\end{figure}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_3f.png}
\end{figure}

The fibers $F$ are a topological space embedded in $E$ on which lie the set of all possible values. For example, if $F$ is the interval $[0, 1]$, then $g(k)$ from equation~\ref{eq:sigma} returns a single measurement $x$ in the interval $F$:
\begin{equation}
    \label{eg:goff}
    g(k) = x, \text{ where } 0\leq x \leq 1
\end{equation}

@@

% schema is ordered list of Column, type is approx F, U cross C over sigma, 
% space of rows/records f:k -> r, sigma:k -> r, is the table function (dataframe as instance)
When $E$ is trivial, then we can decompose $E$ so that each $E$

@@

\subsubsection{Channels}
Acts on different parts of F, types means measurement groups , can be broken out so tau(E_{u} in E)
Tau can preserves the measurement type properties (group scales)
